A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-29 sections/model_overview/main.tex
Address several todos
Address several TODOs (#41)
* Update highlights

* Address several todos

* Add a final TODO to be fixed

* Add example of another application of the model

* Fix a typo

* Add script and notebook of previous plots

* Rename jupyter notebook

* Change plots axis labels

* Scale payoff matrices to be more presentable

* Remove unnecessary equations

* Minor additional changes

* Address the high traffic intensity

\begin{itemize}
    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
    receives and distributes to EDs
    % TODO: Use consistent notation of non-urgent/non-emergency patients
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED 
    \(i\in\{A, B\}\)
    \item \( \mu_i \): The service rate of patients at ED \(i\in\{A, B\}\)
    \item \( C_i \): The number of available resources (healthcare 
    professionals) in the ED \(i\in\{A, B\}\)
    % TODO: Make sure that servers are defined the same way throughout
    \item \( T_i \): The action that ED \(i\in\{A, B\} \) chooses to play which 
    corresponds to the threshold at which they do not accept EMS patients.
    \item \( N_i \): The total patient capacity of the ED \(i\in\{A, B\} \)
    \item \( M_i \): The total parking capacity of the ED \(i\in\{A, B\} \)
    \item \( t \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : Weighted average of blocking time and 
    lost individuals (equation \ref{eq:obj_distributor})
\end{itemize}

@@

Both hospitals follow a queueing model with two waiting spaces for 
individuals. 
The first waiting space (i.e. the waiting space of the hospital) is where the 
patients queue right before receiving 
their service and has a queue capacity of \( N - C \), where \(N\) is the total 
capacity of the hospital and \(C\) is the number of healthcare 
professionals able to see them.
% TODO: Should this be healthcare professionals or available beds?
The second waiting space (i.e. the parking space for ambulances) is where 
ambulances, that are sent from the
ambulance service, stay until their patients are allowed to enter the hospital.
The parking space has a capacity of \(M\) and no servers.
This is shown diagrammatically in Figure~\ref{fig:diagram_of_queueing_system}.

@@

Following this queuing model, the two queueing systems' choice of strategy will 
then rely solely on satisfying their own 
objective, which is to satisfy:

\begin{equation}
    P(W < t) \geq \hat{P}
\end{equation}

where \(W\) is the waiting time of a potential individual, \(t\) is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
For example one approach is to use the threshold that maximises the probability 
that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal \(\hat{P}\).

\begin{equation}
    \arg \max_{T_i} \quad P(W_i < t)
\end{equation}

A more sophisticated objective function would be to get the proportion 
of individuals as close to the percentage aim. 
In other words, to find the threshold that minimises the difference between the 
probability and the percentage goal (or maximise its negation).

% TODO: Maybe only this equation is needed here. Remove the previous two?
\begin{equation}\label{eq:obj_queueing_systems}
    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < t) \right)^2
\end{equation}

>>>>

\begin{itemize}
    \item \( \lambda_2 \): The rate of patients (who can be blocked) that the 
    EMS receives and distributes to EDs
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED 
    \(i\in\{A, B\}\)
    \item \( \mu_i \): The service rate of patients at ED \(i\in\{A, B\}\)
    \item \( C_i \): The number of available resources (healthcare 
    professionals) in the ED \(i\in\{A, B\}\)
    \item \( T_i \): The action that ED \(i\in\{A, B\} \) chooses to play which 
    corresponds to the threshold at which they do not accept EMS patients.
    \item \( N_i \): The total patient capacity of the ED \(i\in\{A, B\} \)
    \item \( M_i \): The total parking capacity of the ED \(i\in\{A, B\} \)
    \item \( t \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : Weighted average of blocking time and 
    lost individuals (equation \ref{eq:obj_distributor})
\end{itemize}

@@

Both hospitals follow a queueing model with two waiting spaces for 
individuals. 
The first waiting space (i.e. the waiting space of the hospital) is where the 
patients queue right before receiving 
their service and has a queue capacity of \( N - C \), where \(N\) is the total 
capacity of the hospital and \(C\) is the number of healthcare 
professionals able to see them.
The second waiting space (i.e. the parking space for ambulances) is where 
ambulances, that are sent from the
ambulance service, stay until their patients are allowed to enter the hospital.
The parking space has a capacity of \(M\) and no servers.
This is shown diagrammatically in Figure~\ref{fig:diagram_of_queueing_system}.

@@

Following this queueing model, the two queueing systems' choice of strategy will 
then rely solely on satisfying their own objective.
The objective function is defined as:

\begin{equation}\label{eq:obj_queueing_systems}
    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < t) \right)^2 \qquad 
    i \in {A, B}
\end{equation}

where \(W\) is the waiting time of a potential individual, \(t\) is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
In other words, their aim is to find the threshold that minimises the 
difference between the probability \(P(W_i < t)\) and the percentage goal 
(or maximise its negation).
